---
name: Abhijit
surname: Dasgupta
#position: "Professor"
address: "12410 Milestone Manor Lane, Germantown MD 20876"
phone: "(240) 813-8458"
www: webbedfeet.netlify.com
email: "adasgupta@araastat.com"
twitter: webbedfeet
github: webbedfeet
# linkedin:
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: true
    includes:
      before_body: ["pmid.tex","name_bold.tex"]
  vitae::hyndman:
    keep_tex: true
    includes:
      before_body: ["pmid.tex","name_bold.tex"]
headcolor: 414141
fontsize: "11pt"
geometry: letter,margin=1in
# docname: "Resume"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = T)
library(vitae)
library(here)
suppressPackageStartupMessages(library(tidyverse))
source(here('CV', 'baretable.R'))
```

# Summary

I am an experienced statistician and data scientist interested in
multidisciplinary collaborations to understand and solve problems using modern
data analytic tools and techniques. I am also interested in the mentoring,
education and training of the next generation of data scientists.

# Education

```{r education}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "B.Stat.(Hons.)", '1993', 'Indian Statistical Institute','Kolkata, India',
  'M.S. in Statistics', '1995','University of Washington','Seattle, WA',
  'Ph.D. in Biostatistics','2001','University of Washington','Seattle, WA'
) %>% 
  detailed_entries(Degree, Year, Institution, Where, why=NULL)
  # detailed_entries(Degree, Year, Institution, Where)
```

# Current Positions
```{r jobs, results='asis'}
tribble(
  ~Start, ~Position, ~Organization,
  2009, "Director and Chief Data Scientist", "ARAASTAT, Germantown, MD",
  2010, "Consultant Biostatistician", "National Institute for Arthritis, Musculoskeletal and Skin Diseases",
    2010, "Consultant Biostatistician", "National Institutes of Health, Bethesda, MD",
  2011, "Chief Data Scientist and Co-Founder", "Zansors, Arlington, VA",
  2016, "Affiliate Faculty", "Department of Systems Biology",
  2016, "Affiliate Faculty", "George Mason University, Fairfax, VA",
  2018, "Co-chairman", "Department of Bioinformatics and Data Science",
  2018, "Co-chairman", "FAES Graduate School at NIH"
) %>% 
  mutate(Start = paste0(Start, '--')) %>% 
  mutate(Position = glue::glue("\\textbf{{{Position}}}")) %>% 
  gather(unit, value, -Start) %>%
  arrange(Start, desc(unit)) %>% 
  distinct() %>% 
  mutate(Start = ifelse(unit=='Organization','', Start)) %>% 
  select(-unit) %>% 
  baretable()
  
  # baretable()
  # brief_entries(Position, Start, Organization)
# detailed_entries(Position, Start, Organization, where = "", why = "")
```

\newpage
# Recent Teaching

I am a [Carpentries](https://www.carpentries.org)-certified instructor with extensive experience 
teaching data science using R and Python to a wide variety of corporate,
government and academic audiences. My classes have included programming neophytes as well as 
experienced analysts looking to enhance their skills. Workshop and training clients include Freddie Mac, the State Department and Brookings Institute. I regular teach R classes at NIH.

```{r teaching, results='asis'}
tribble(
  ~Start, ~Course, ~Location, ~Notes, ~URL,
  "2019 -- present", "Data Visualization using R", "FAES, NIH", "","http://www.araastat.com/BIOF439",
  "2019", "Programming with R", "Foreign Service Institute, Department of State","3-day workshops introducing R in a Excel-dominant environment","",
  "2018", "SQL for Programmers", "Brookings Institute","","",
  "2018 -- present", "Carpentries Workshops", "NIH and other locations", "both R- and Python-based", "",
  "2017", "Machine Learning using Python", "Freddie Mac", "This is a 32-hour corporate training program covering the background, theory, usage ", "",
  "2017", "Machine Learning using Python", "Freddie Mac", "and implementation of several machine learning methods","",
  "2017", "Best Practices in Data Analysis", "Joint Statistical Meetings, Baltimore", "This is a continuing education course. I received all A's on my evaluations","",
  "2016 -- present", "Practical R", "FAES, NIH", "Introductory R course", "http://www.araastat.com/BIOF339_PracticalR"
) %>% 
  mutate(Course = ifelse(URL=="",glue::glue("\\textbf{{{Course}}}"), 
                         glue::glue("\\href{{{URL}}}{{\\textbf{{{Course}}}}}"))) %>% 
  mutate(Notes = ifelse(Notes == '', '', glue::glue("\\emph{{{Notes}}}"))) %>% 
  mutate(Description = paste(Course, Location, sep = ', ')) %>% 
  select( -Location, -URL) %>% 
  group_by(Course) %>% 
  tidyr::gather(unit, value, -Start, -Course) %>% 
  arrange(desc(Start), Course, unit) %>% 
  mutate(Start = ifelse(unit == 'Notes','', Start)) %>% 
  filter(value != '') %>% 
  ungroup() %>% 
  distinct() %>% 
  select(Start, value) %>% 
  baretable()
  # mutate(Start= ifelse(Notes == '', Start, ''))
  # select(Start, Description) %>% 
  # baretable()
```

# Professional Service

1. Member, NIH SBIR review committees related to neurobiology
1. Member, Data Safety Monitoring Boards, National Institute of Mental Heath, NIH
1. Reviewer for various academic journals. 

# Professional Memberships

1. American Statistical Association 
 
# Community Leadership

```{r leader, results='asis'}
tribble(
  ~Years, ~Position, ~Organization, ~Notes,
  '2011 --', 'Co-organizer', 'Statistical Programming DC', "Originally the DC R Users Group, this meetup brings together",
  '2011 --', "Co-organizer","Statistical Programming DC", "the DC data science community to share and discuss data science implementations in R and Python",
  '2018-2019', 'Board of Directors', '\\href{http://www.sanskriti-dc.org}{Sanskriti, Inc.}', 'A socio-cultural organization supporting the Bengali community',
  '2018-2019', 'Board of Directors', '\\href{http://www.sanskriti-dc.org}{Sanskriti, Inc.}', 'in Montgomery County and the greater DC area',
  "2013-2016","Board of Directors", "\\href{https://www.datacommunitydc.org}{Data Community DC}",""
) %>% 
  mutate(Position = glue::glue("\\textbf{{{Position}}}")) %>% 
  mutate(Notes = ifelse(Notes=='', Notes, glue::glue("\\emph{{{Notes}}}"))) %>% 
  tidyr::unite('Description', c('Position','Organization'), sep = ', ') %>% 
  group_by(Years) %>% 
  gather(unit, value, -Years) %>%
  arrange(desc(Years), unit) %>% 
  ungroup() %>% 
  distinct() %>% 
  mutate(Years = ifelse(unit=='Notes', '', Years)) %>% 
  filter(value!='') %>% 
  select(-unit) %>% 
  baretable()

```

\newpage
# Publications

```{r scholars, eval=F}
scholar::get_publications("EgaGUCwAAAAJ") %>% 
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal,
    why = cites
  ) %>% 
  arrange(desc(when))
```

## Ph.D. Thesis

```{r thesis}
b1 <- bibliography_entries(here('pubmed.bib')) %>% select(-month)
b1 %>% dplyr::filter(bibtype=='PhdThesis')
```

## Books

```{r books}
b1 %>% dplyr::filter(bibtype=='Book') %>% arrange(desc(year))
```

## Articles

```{r articles}
abstract_keys <- c("Ward:2018c", "Holzinger2016", "Sheth2007", "Shamimi-Noori2007", "Tektonidou2015a", "Gibbons2009", "Natan2009", "Gibbons2009a", "Brody2009", "Bonita2009", "Ruggiero2009")


b1 %>% dplyr::filter(bibtype=='Article') %>%
  dplyr::filter(!(key %in% abstract_keys)) %>%
  select(key, bibtype, title, year, author, journal, pmid, pmcid) %>%
  arrange(desc(year))

```

## Abstracts

```{r abstracts}
b1 %>% dplyr::filter(key %in% abstract_keys) %>% arrange(desc(year))
```

\newpage
## Current projects

```{r current}
b1 %>% dplyr::filter(bibtype=='Unpublished') %>% arrange(desc(year))
```

