---
name: Abhijit
surname: Dasgupta
position: "Statistician/Data Scientist"
qualifications: "Ph.D."
#position: "Professor"
address: "12410 Milestone Manor Lane, Germantown MD 20876"
phone: "+1 (240) 813-8458"
www: webbedfeet.netlify.com
email: "adasgupta@araastat.com"
twitter: webbedfeet
github: webbedfeet
# linkedin:
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: true
    includes:
      before_body: ["pmid.tex","name_bold.tex"]
  vitae::hyndman:
    keep_tex: true
    includes:
      before_body: ["pmid.tex","name_bold.tex"]
headcolor: 414141
fontsize: "11pt"
geometry: letter,margin=1in
# docname: "Resume"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = T)
library(vitae)
library(here)
suppressPackageStartupMessages(library(tidyverse))
source(here('CV', 'baretable.R'))
```

# Summary

I am an expert statistician and data scientist interested in
multidisciplinary collaborations to understand and solve problems using modern
data analytic tools and techniques. I work at the interface of statistics and machine learning, and have extensive experience (SME) in statistical methods, study design, machine learning and data visualization. I am an expert in using R and Python for data analytics and data science applied to a wide variety of disciplines, with over 20 years experience. I am an excellent communicator and teacher who can explain technical details well to a non-technical audience. I am also interested in the mentoring,
education and training of the next generation of data scientists.

# Education and Training

```{r education}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,~What,
  "B.Stat.(Hons.)", '1993', 'Indian Statistical Institute','Kolkata, India',NA,
  'M.S. in Statistics', '1995','University of Washington','Seattle, WA',NA,
  'Ph.D. in Biostatistics','2001','University of Washington','Seattle, WA',NA,
  'Post-doctoral training','2001-2006','National Cancer Institute','Bethesda, MD','Genetic epidemiology, statistical genetics, bioinformatics'
) %>% 
  detailed_entries(Degree, Year, Institution, Where, why=What)
  # detailed_entries(Degree, Year, Institution, Where)
```

# Current Positions
```{r jobs, results='asis'}
tribble(
  ~Start, ~Position, ~Organization,~Where, ~Description,
  2009, "Director and Chief Data Scientist", "ARAASTAT", "Germantown, MD", "Statistics and Data Science consultant",
  2009, "Director and Chief Data Scientist", "ARAASTAT", "Germantown, MD","Statistical and predictive analytics, data visualization",
  2009, "Director and Chief Data Scientist", "ARAASTAT", "Germantown, MD","Grant writing",
  2010, "Consultant Biostatistician (Kelly Government Services)", "National Institute for Arthritis, Musculoskeletal and Skin Diseases, NIH", "Bethesda, MD","Statistical and Machine Learning analyses with applications in Rheumatology",
  2010, "Consultant Biostatistician (Kelly Government Services)", "National Institute for Arthritis, Musculoskeletal and Skin Diseases, NIH", "Bethesda, MD","Computational statistics, Bayesian methods, machine learning, simulation, survival analysis, regression, visualization",
  2010, "Consultant Biostatistician (Kelly Government Services)", "National Institute for Arthritis, Musculoskeletal and Skin Diseases, NIH", "Bethesda, MD","Clinical trials, large administrative databases (Medicare, NIS, NHANES)",
  2011, "Chief Data Scientist and Co-Founder", "Zansors", "Arlington, VA","Lead technical efforts in R&D, product development",
  2011, "Chief Data Scientist and Co-Founder", "Zansors", "Arlington, VA","Algorithms, signal processing, analytics, data visualization",
  2011, "Chief Data Scientist and Co-Founder", "Zansors", "Arlington, VA","Work with engineers, app developers, UI/UX experts, business leaders",
  2016, "Affiliate Faculty", "Department of Systems Biology, George Maon University", "Fairfax, VA",NA,
  2018, "Co-chairman", "Department of Bioinformatics and Data Science, FAES Graduate School at NIH","Bethesda, MD", "Oversee the data science and bioinformatics cirruculum",
  2018, "Co-chairman", "Department of Bioinformatics and Data Science, FAES Graduate School at NIH","Bethesda, MD","Teach two high-demand classes on R (Practical R, and Data Visualization using R)",
) %>% 
  mutate(Start = paste0(Start, '--')) %>% 
  # mutate(Position = glue::glue("\\textbf{{{Position}}}")) %>% 
  # gather(unit, value, -Start) %>%
  # arrange(Start, desc(unit)) %>% 
  # distinct() %>% 
  # mutate(Start = ifelse(unit=='Organization','', Start)) %>% 
  # select(-unit) %>% 
  # baretable()
  detailed_entries(what = Position, when=Start, with=Organization, where = Where, why=Description)
  
  # baretable()
  # brief_entries(Position, Start, Organization)
# detailed_entries(Position, Start, Organization, where = "", why = "")
```

\newpage
# Recent Teaching

I am a [Carpentries](https://www.carpentries.org)-certified instructor with extensive experience 
teaching data science using R and Python to a wide variety of corporate,
government and academic audiences. My classes have included programming neophytes as well as 
experienced analysts looking to enhance their skills. Workshop and training clients include Freddie Mac, the State Department and Brookings Institute. I regular teach R classes at NIH.

```{r teaching, results='asis'}
tribble(
  ~Start, ~Course, ~Location, ~Notes, ~URL,
  "2019 -- present", "Data Visualization using R", "FAES, NIH", "","http://www.araastat.com/BIOF439",
  "2019", "Programming with R", "Foreign Service Institute, Department of State","3-day workshops introducing R in a Excel-dominant environment","",
  "2018", "SQL for Programmers", "Brookings Institute","","",
  "2018 -- present", "Carpentries Workshops", "NIH and other locations", "both R- and Python-based", "",
  "2017", "Machine Learning using Python", "Freddie Mac", "This is a 32-hour corporate training program covering the background, theory, usage ", "",
  "2017", "Machine Learning using Python", "Freddie Mac", "and implementation of several machine learning methods","",
  "2017", "Best Practices in Data Analysis", "Joint Statistical Meetings, Baltimore", "This is a continuing education course. I received all A's on my evaluations","",
  "2016 -- present", "Practical R", "FAES, NIH", "Introductory R course", "http://www.araastat.com/BIOF339_PracticalR"
) %>% 
  mutate(Course = ifelse(URL=="",glue::glue("\\textbf{{{Course}}}"), 
                         glue::glue("\\href{{{URL}}}{{\\textbf{{{Course}}}}}"))) %>% 
  mutate(Notes = ifelse(Notes == '', '', glue::glue("\\emph{{{Notes}}}"))) %>% 
  mutate(Description = paste(Course, Location, sep = ', ')) %>% 
  select( -Location, -URL) %>% 
  group_by(Course) %>% 
  tidyr::gather(unit, value, -Start, -Course) %>% 
  arrange(desc(Start), Course, unit) %>% 
  mutate(Start = ifelse(unit == 'Notes','', Start)) %>% 
  filter(value != '') %>% 
  ungroup() %>% 
  distinct() %>% 
  select(Start, value) %>% 
  baretable()
  # mutate(Start= ifelse(Notes == '', Start, ''))
  # select(Start, Description) %>% 
  # baretable()
```

# Professional Service

1. Member, NIH SBIR review committees related to neurobiology
1. Member, Data Safety Monitoring Boards, National Institute of Mental Heath, NIH
1. Reviewer for various academic journals. 

# Professional Memberships

1. American Statistical Association 
 
# Community Leadership

```{r leader, results='asis'}
tribble(
  ~Years, ~Position, ~Organization, ~Notes,
  '2011 --', 'Co-organizer', 'Statistical Programming DC', "Originally the DC R Users Group, this meetup brings together",
  '2011 --', "Co-organizer","Statistical Programming DC", "the DC data science community to share and discuss data science implementations in R and Python",
  '2018-2019', 'Board of Directors', '\\href{http://www.sanskriti-dc.org}{Sanskriti, Inc.}', 'A socio-cultural organization supporting the Bengali community',
  '2018-2019', 'Board of Directors', '\\href{http://www.sanskriti-dc.org}{Sanskriti, Inc.}', 'in Montgomery County and the greater DC area',
  "2013-2016","Board of Directors", "\\href{https://www.datacommunitydc.org}{Data Community DC}",""
) %>% 
  mutate(Position = glue::glue("\\textbf{{{Position}}}")) %>% 
  mutate(Notes = ifelse(Notes=='', Notes, glue::glue("\\emph{{{Notes}}}"))) %>% 
  tidyr::unite('Description', c('Position','Organization'), sep = ', ') %>% 
  group_by(Years) %>% 
  gather(unit, value, -Years) %>%
  arrange(desc(Years), unit) %>% 
  ungroup() %>% 
  distinct() %>% 
  mutate(Years = ifelse(unit=='Notes', '', Years)) %>% 
  filter(value!='') %>% 
  select(-unit) %>% 
  baretable()

```

\newpage
# Publications

```{r scholars, eval=F}
scholar::get_publications("EgaGUCwAAAAJ") %>% 
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal,
    why = cites
  ) %>% 
  arrange(desc(when))
```

## Ph.D. Thesis

```{r thesis, eval=T}
b1 <- bibliography_entries(here('pubmed.bib')) %>% select(-month)
b1 %>% dplyr::filter(bibtype=='PhdThesis')
```

## Books

```{r books, eval=T}
b1 %>% dplyr::filter(bibtype=='Book') %>% arrange(desc(year))
```

## Articles

```{r articles, eval=T}
abstract_keys <- c("Ward:2018c", "Holzinger2016", "Sheth2007", "Shamimi-Noori2007", "Tektonidou2015a", "Gibbons2009", "Natan2009", "Gibbons2009a", "Brody2009", "Bonita2009", "Ruggiero2009")


b1 %>% dplyr::filter(bibtype=='Article') %>%
  dplyr::filter(!(key %in% abstract_keys)) %>%
  select(key, bibtype, title, year, author, journal, pmid, pmcid) %>%
  arrange(desc(year))

```

## Abstracts

```{r abstracts, eval=T}
b1 %>% dplyr::filter(key %in% abstract_keys) %>% arrange(desc(year))
```

\newpage
## Current projects

```{r current, eval=T}
b1 %>% dplyr::filter(bibtype=='Unpublished') %>% arrange(desc(year))
```

