---
name: Abhijit
surname: Dasgupta
position: "Data Scientist"
qualifications: "Ph.D."
#position: "Professor"
address: "12410 Milestone Manor Lane, Germantown MD 20876"
phone: "+1 (240) 813-8458"
# www: webbedfeet.netlify.app
email: "adasgupta@araastat.com"
twitter: webbedfeet
github: webbedfeet
linkedin: abhijit-dasgupta-70197713
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::hyndman:
    keep_tex: true
    latex_engine: xelatex
    pandoc_args:
      - --lua-filter=_extensions/pandoc-ext/section-bibliographies/section-bibliographies.lua
      # - --lua-filter=bold-author.lua
    # includes:
    #   before_body: ["name_bold.tex"]
      # before_body: ["pmid.tex","name_bold.tex"]
  vitae::awesomecv:
    keep_tex: true
    # includes:
      # before_body: ["pmid.tex","name_bold.tex"]
      # before_body: ["name_bold.tex"]
papersize: letterpaper
docname: "Cirruculum vitae"
awesomecolor: awesome-orange
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = F)
library(vitae)
library(here)
suppressPackageStartupMessages(library(tidyverse))
source(here('CV', 'baretable.R'))
```

# Summary

I am an expert statistician and data scientist interested in
multidisciplinary collaborations to understand and solve problems using modern
data analytic tools and techniques. I work at the interface of statistics and machine learning, and have extensive experience (SME) in statistical methods, study design, machine learning, Bayesian analyses and data visualization. I am an expert in using R and Python for data analytics and data science applied to a wide variety of disciplines, with over 20 years experience. I am an excellent communicator and teacher who can explain technical details well to a non-technical audience, while maintaining rigor in the analytic techniques used. I am also interested in the mentoring,
education and training of the next generation of data scientists.


# Current Positions

## Primary

```{r jobs1, results = 'asis'}
tribble(
  ~Start, ~Position, ~Organization,~Where, ~Description,
  2025, "Data Science Director", "AstraZeneca", "Gaithersburg, MD", "Oncology biomarker development using statistics and machine learning",
  2025, "Data Science Director", "AstraZeneca", "Gaithersburg, MD", "Survival analysis, Bayesian modeling",
  2020, "Data Science Associate Director", "AstraZeneca", "Gaithersburg, MD", "Biostatistics, machine learning and AI collaboration across therapeutic areas in oncology",
  2020, "Data Science Associate Director", "AstraZeneca", "Gaithersburg, MD", "Survival analysis, machine learning, biomarker discovery and development",
  2020, 'Adjunct Professor', 'Georgetown University','Washington DC', 'Data visualization (DSAN 5200)',
  2020, 'Adjunct Professor', 'Georgetown University','Washington DC', 'Big Data and Cloud Computing (DSAN 6000)',
  2020, 'Adjunct Professor', 'Georgetown University','Washington DC', 'Biological and Biomedical Data Science (DSAN 6150)',
) %>% 
  mutate(Start = paste0(Start, '--')) %>% 
  detailed_entries(what = Position, when=Start, with=Organization, where = Where, why=Description)


```

## Other

```{r jobs, results='asis'}
tribble(
  ~Start, ~Position, ~Organization,~Where, ~Description,
  2009, "Director and Chief Data Scientist", "ARAASTAT", "Germantown, MD", "Statistics and Data Science consultant",
  2009, "Director and Chief Data Scientist", "ARAASTAT", "Germantown, MD","Statistical and predictive analytics, data visualization",
  2009, "Director and Chief Data Scientist", "ARAASTAT", "Germantown, MD","R and Python training for Data Science and Machine Learning",
  2016, "Affiliate Faculty", "Department of Systems Biology, George Mason University", "Fairfax, VA",NA,
  2020, "Adjunct Faculty", "Data Science and Analytics, Georgetown University", "Washington, DC", NA, 
  2026, "Adjunct Faculty", "Data Science, George Washington University", "Washington, DC", NA
) %>% 
  mutate(Start = paste0(Start, '--')) %>% 
  detailed_entries(what = Position, when=Start, with=Organization, where = Where, why=Description)
  
```

# Recent Teaching

I am a [Carpentries](https://www.carpentries.org)-certified instructor with
extensive experience teaching data science using R and Python to a wide variety
of corporate, government and academic audiences. My classes have included
programming neophytes as well as experienced analysts looking to enhance their
skills. Workshop and training clients include Freddie Mac, the State Department
and Brookings Institute. I regularly lead highly-rated R-based training at
AstraZeneca and help organize internal data science forums and conferences.


```{r teaching, results='asis'}
tribble(
  ~Start, ~Course, ~Location, ~Notes, ~URL,
  "2026 -- present", "Applied Big Data Analytics", "George Washington University", "", "",
  "2024 -- present", "Biological and Biomedical Data Science", "Georgetown University", "", "",
  "2024 -- present", "Data Visualization using R", "AstraZeneca", "", "",
  "2020-2023", "Practical R", "AstraZeneca", "", "",
  "2020 -- 2025", "Advanced Data Visualization", "Georgetown University", "", "",
  "2020 -- 2024", "Big Data Analytics and Cloud Computing", "Georgetown University", "","",
  "2021", "Data Science using Python", "FAES, NIH", "A 3-day online workshop introducing data science", "https://www.araastat.com/BIOF085",
  "2021", "Data Visualization using Python", 'FAES, NIH', '', 'https://www.araastat.com/BIOF440',
  "2019 -- 2020", "Data Visualization using R", "FAES, NIH", "","https://www.araastat.com/BIOF439",
  "2019", "Programming with R", "Foreign Service Institute, Department of State","3-day workshops introducing R in a Excel-dominant environment","",
  "2018", "SQL for Programmers", "Brookings Institute","","",
  "2018 -- 2022", "Carpentries Workshops", "NIH and other locations", "both R- and Python-based", "",
  "2017", "Machine Learning using Python", "Freddie Mac", "This is a 32-hour corporate training program covering the background, theory, usage ", "",
  "2017", "Machine Learning using Python", "Freddie Mac", "and implementation of several machine learning methods","",
  "2017", "Best Practices in Data Analysis", "Joint Statistical Meetings, Baltimore", "This is a continuing education course. I received all A's on my evaluations","",
  "2016 -- 2020", "Practical R", "FAES, NIH", "Introductory R course", "https://www.araastat.com/BIOF339"
) %>% 
  mutate(Course = ifelse(URL=="",glue::glue("\\textbf{{{Course}}}"), 
                         glue::glue("\\href{{{URL}}}{{\\textbf{{{Course}}}}}"))) %>% 
  mutate(Notes = ifelse(Notes == '', '', glue::glue("\\emph{{{Notes}}}"))) %>% 
  mutate(Description = paste(Course, Location, sep = ', ')) %>% 
  select( -Location, -URL) %>% 
  group_by(Course) %>% 
  tidyr::gather(unit, value, -Start, -Course) %>% 
  arrange(desc(Start), Course, unit) %>% 
  mutate(Start = ifelse(unit == 'Notes','', Start)) %>% 
  filter(value != '') %>% 
  ungroup() %>% 
  distinct() %>% 
  select(Start, value) %>% 
  baretable()
  # mutate(Start= ifelse(Notes == '', Start, ''))
  # select(Start, Description) %>% 
  # baretable()
```

# Education and Training

```{r education}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,~What,
  "B.Stat.(Hons.)", '1993', 'Indian Statistical Institute','Kolkata, India',NA,
  'M.S. in Statistics', '1995','University of Washington','Seattle, WA',NA,
  'Ph.D. in Biostatistics','2001','University of Washington','Seattle, WA',NA,
  'Post-doctoral training','2001-2006','National Cancer Institute','Bethesda, MD','Genetic epidemiology, statistical genetics, bioinformatics'
) %>% 
  detailed_entries(Degree, Year, Institution, Where, why=What)
  # detailed_entries(Degree, Year, Institution, Where)
```


# Work History

```{r previous,results='asis'}
tribble(
  ~Start, ~Position, ~Organization,~Where, ~Description,
  '2018-2021', "Co-chairman", "Department of Bioinformatics and Data Science, FAES Graduate School at NIH","Bethesda, MD", "Oversee the data science and bioinformatics cirruculum",
  '2018-2021', "Co-chairman", "Department of Bioinformatics and Data Science, FAES Graduate School at NIH","Bethesda, MD","Teach  high-demand classes on R (Practical R, and Data Visualization using R) and Python (Data Visualization using Python)",
  '2011-2020', "Chief Data Scientist and Co-Founder", "Zansors", "Arlington, VA","Lead technical efforts in R&D, product development",
  '2011-2020', "Chief Data Scientist and Co-Founder", "Zansors", "Arlington, VA","Algorithms, signal processing, analytics, data visualization",
  '2011-2020', "Chief Data Scientist and Co-Founder", "Zansors", "Arlington, VA","Work with engineers, app developers, UI/UX experts, business leaders",
    '2010-2020', "Biostatistician (contractor with Kelly Government Services)", "National Institute for Arthritis, Musculoskeletal and Skin Diseases, NIH", "Bethesda, MD","Statistical and Machine Learning analyses with applications in Rheumatology",
  '2010-2020', "Biostatistician (contractor with Kelly Government Services)", "National Institute for Arthritis, Musculoskeletal and Skin Diseases, NIH", "Bethesda, MD","Computational statistics, Bayesian methods, machine learning, simulation, survival analysis, regression, visualization",
  '2010-2020', "Biostatistician (contractor with Kelly Government Services)", "National Institute for Arthritis, Musculoskeletal and Skin Diseases, NIH", "Bethesda, MD","Clinical trials, large administrative databases (Medicare, NIS, NHANES)",
  '2009-2012', 'Director, Machine Learning','Tranzxn, LLC', 'Gaithersburg, MD', 'Developing models for predicting hospital acquired conditions',
  '2006-2009', 'Assistant Professor', 'Division of Biostatistics, Thomas Jefferson University', 'Philadelphia, PA','Biostatistics, Bioinformatics, Oncology',
  '2006-2009', 'Assistant Professor', 'Division of Biostatistics, Thomas Jefferson University', 'Philadelphia, PA','Supported the Kimmel Cancer Center'
) %>% 
  detailed_entries(what = Position, when=Start, with=Organization, where = Where, why=Description)
```




# Professional Service

1. Member, Data Safety Monitoring Boards, National Institute of Mental Heath, NIH
1. Member, NIH SBIR review committees related to neurobiology
1. Reviewer for various academic journals. 

# Professional Memberships

1. American Statistical Association 
 
# Community Leadership

```{r leader, results='asis'}
tribble(
  ~Years, ~Position, ~Organization, ~Notes,
  '2011-2020', 'Co-organizer', 'Statistical Programming DC', "Originally the DC R Users Group, this meetup brings together",
  '2011-2020', "Co-organizer","Statistical Programming DC", "the DC data science community to share and discuss data science implementations in R and Python",
  '2018-2019', 'Board of Directors', '\\href{http://www.sanskriti-dc.org}{Sanskriti, Inc.}', 'A socio-cultural organization supporting the Bengali community',
  '2018-2019', 'Board of Directors', '\\href{http://www.sanskriti-dc.org}{Sanskriti, Inc.}', 'in Montgomery County and the greater DC area',
  "2013-2016","Board of Directors", "\\href{https://www.datacommunitydc.org}{Data Community DC}",""
) %>% 
  mutate(Position = glue::glue("\\textbf{{{Position}}}")) %>% 
  mutate(Notes = ifelse(Notes=='', Notes, glue::glue("\\emph{{{Notes}}}"))) %>% 
  tidyr::unite('Description', c('Position','Organization'), sep = ', ') %>% 
  group_by(Years) %>% 
  gather(unit, value, -Years) %>%
  arrange(desc(Years), unit) %>% 
  ungroup() %>% 
  distinct() %>% 
  mutate(Years = ifelse(unit=='Notes', '', Years)) %>% 
  filter(value!='') %>% 
  select(-unit) %>% 
  baretable()

```

# Publications

## Ph.D. Thesis

```{r}
bl <- bibliography_entries(here('publications.bib'))
bl |> filter(type=='thesis')
```

## Books

```{r}
bl %>% dplyr::filter(type=='book') %>% arrange(desc(issued))
```

## Articles

I have `r bl |> filter(type=='article-journal') |> nrow()` peer-reviewed publications and abstracts.  A full listing and citation statistics are available at my [Google Scholar page](https://scholar.google.com/citations?user=EgaGUCwAAAAJ&hl=en){target="_blank"}  
\vspace{0.5cm}

```{r, eval = FALSE}
bl |> filter(type=='article-journal') |> arrange(desc(issued)) |> select(-URL)
```



# Publications


```{r readbib, eval=F}
b1 <- bibliography_entries(here('publications.bib')) 
# b1 <- bibliography_entries(here('pubmed.bib'))
# b1 <- as.data.frame(RefManageR::ReadBib(here('pubmed.bib')))
```

## Ph.D. Thesis

```{r thesis, eval=F}
b1 %>% dplyr::filter(type=='thesis')
```

## Books

```{r books, eval=F}
b1 %>% dplyr::filter(type=='book') %>% arrange(desc(issued))
```

## Articles

```{r articles, eval=F}
abstract_keys <- c("Ward:2018c", "Holzinger2016", "Sheth2007", "Shamimi-Noori2007", "Tektonidou2015a", "Gibbons2009", "Natan2009", "Gibbons2009a", "Brody2009", "Bonita2009", "Ruggiero2009")


b1 %>% dplyr::filter(type=='article-journal') %>%
  # dplyr::filter(!(key %in% abstract_keys)) %>%
  select(id, type, title, issued, author, `container-title-short`, PMID, PMCID) %>%
  arrange(desc(issued)) 

```

## Abstracts

```{r abstracts, eval=F}
b1 %>% dplyr::filter(key %in% abstract_keys) %>% arrange(desc(year))
```

## Manuscripts in progress

```{r current, eval=F}
b1 %>% dplyr::filter(bibtype=='Unpublished') %>% arrange(desc(year))
```

--> 
