---
name: Abhijit
surname: Dasgupta
position: "Statistician/Data Scientist"
qualifications: "Ph.D."
#position: "Professor"
address: "12410 Milestone Manor Lane, Germantown MD 20876"
phone: "+1 (240) 813-8458"
www: webbedfeet.netlify.com
email: "adasgupta@araastat.com"
twitter: webbedfeet
github: webbedfeet
# linkedin:
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: true
    includes:
      before_body: ["pmid.tex","name_bold.tex"]
  vitae::hyndman:
    keep_tex: true
    includes:
      before_body: ["pmid.tex","name_bold.tex"]
headcolor: 414141
fontsize: "12pt"
geometry: letter,margin=1in
# docname: "Resume"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = T)
library(vitae)
library(here)
suppressPackageStartupMessages(library(tidyverse))
source(here('CV', 'baretable.R'))
```

# Summary

I am an expert statistician and data scientist interested in
multidisciplinary collaborations to understand and solve problems using modern
data analytic tools and techniques. I work at the interface of statistics and machine learning, and have extensive experience (SME) in statistical methods, study design, machine learning and data visualization. I am an expert in using R and Python for data analytics and data science applied to a wide variety of disciplines, with over 20 years experience. I am an excellent communicator and teacher who can explain technical details well to a non-technical audience. I am also interested in the mentoring,
education and training of the next generation of data scientists.

# Education and Training

```{r education}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,~What,
  "B.Stat.(Hons.)", '1993', 'Indian Statistical Institute','Kolkata, India',NA,
  'M.S. in Statistics', '1995','University of Washington','Seattle, WA',NA,
  'Ph.D. in Biostatistics','2001','University of Washington','Seattle, WA',NA,
  'Post-doctoral training','2001-2006','National Cancer Institute','Bethesda, MD','Genetic epidemiology, statistical genetics, bioinformatics'
) %>% 
  detailed_entries(Degree, Year, Institution, Where, why=What)
  # detailed_entries(Degree, Year, Institution, Where)
```

# Current Positions


```{r jobs1, results = 'asis'}
tribble(
  ~Start, ~Position, ~Organization,~Where, ~Description,
  2010, "Biostatistician (contractor with Kelly Government Services)", "National Institute for Arthritis, Musculoskeletal and Skin Diseases, NIH", "Bethesda, MD","Statistical and Machine Learning analyses with applications in Rheumatology",
  2010, "Biostatistician (contractor with Kelly Government Services)", "National Institute for Arthritis, Musculoskeletal and Skin Diseases, NIH", "Bethesda, MD","Computational statistics, Bayesian methods, machine learning, simulation, survival analysis, regression, visualization",
  2010, "Biostatistician (contractor with Kelly Government Services)", "National Institute for Arthritis, Musculoskeletal and Skin Diseases, NIH", "Bethesda, MD","Clinical trials, large administrative databases (Medicare, NIS, NHANES)",
) %>% 
  mutate(Start = paste0(Start, '--')) %>% 
  detailed_entries(what = Position, when=Start, with=Organization, where = Where, why=Description)


```

## Other

```{r jobs, results='asis'}
tribble(
    ~Start, ~Position, ~Organization,~Where, ~Description,
  2018, "Co-chairman", "Department of Bioinformatics and Data Science, FAES Graduate School at NIH","Bethesda, MD", "Oversee the data science and bioinformatics cirruculum",
  2018, "Co-chairman", "Department of Bioinformatics and Data Science, FAES Graduate School at NIH","Bethesda, MD","Teach two high-demand classes on R (Practical R, and Data Visualization using R)"
) %>% 
  mutate(Start = paste0(Start, '--')) %>% 
  detailed_entries(what = Position, when=Start, with=Organization, where = Where, why=Description)
  
```


# Professional Service

1. Member, NIH SBIR review committees related to neurobiology
1. Member, Data Safety Monitoring Boards, National Institute of Mental Heath, NIH
1. Reviewer for various academic journals. 

# Professional Memberships

1. American Statistical Association 
 

\newpage
# Publications


```{r readbib, eval=T}
b1 <- bibliography_entries(here('pubmed.bib')) %>% select(-month)

```

## Ph.D. Thesis

```{r thesis, eval=T}
b1 %>% dplyr::filter(bibtype=='PhdThesis')
```

## Books

```{r books, eval=T}
b1 %>% dplyr::filter(bibtype=='Book') %>% arrange(desc(year))
```

## Articles

```{r articles, eval=T}
abstract_keys <- c("Ward:2018c", "Holzinger2016", "Sheth2007", "Shamimi-Noori2007", "Tektonidou2015a", "Gibbons2009", "Natan2009", "Gibbons2009a", "Brody2009", "Bonita2009", "Ruggiero2009")


b1 %>% dplyr::filter(bibtype=='Article') %>%
  dplyr::filter(!(key %in% abstract_keys)) %>%
  select(key, bibtype, title, year, author, journal, pmid, pmcid) %>%
  arrange(desc(year)) 

```

## Abstracts

```{r abstracts, eval=T}
b1 %>% dplyr::filter(key %in% abstract_keys) %>% arrange(desc(year))
```


## Current projects

```{r current, eval=T}
b1 %>% dplyr::filter(bibtype=='Unpublished') %>% arrange(desc(year))
```

